Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-04 paper.tex
Modified "Method" introduction

The iRail API is a XML/JSON HTTP API where each request on \url{http://api.irail.be} returns a response that can be used directly in an end-user app.
It contains four features: 
\begin{itemize}
\item Route Planning Feature (\url{http://api.irail.be/connections/{?from,to,date,time}}).
\item Next Departures Feature (\url{http://api.irail.be/liveboard/{?station,date,time}}).
\item Train Status Feature query (\url{http://api.irail.be/vehicle/{?id,date}}).
\item List All Stations Feature (\url{http://api.irail.be/stations/}).
\end{itemize}

@@

We have gathered the \emph{Apache} \emph{access.log} files generated between 2012 and 2015 containing: 
\begin{itemize}
  \item Timestamp,
  \item HTTP Status Code,
  \item Request Path (e.g., \url{/connections/?from=Ghent\&to=Antwerp})
  \item User-Agent (cfr. RFC2616\footnote{The User-Agent request-header field contains information about the user agent originating the request. This is for statistical purposes, the tracing of protocol violations, and automated recognition of user agents for the sake of tailoring responses to avoid particular user agent limitations -- \url{http://www.w3.org/Protocols/rfc2616/rfc2616-sec14.html}})
\end{itemize}

@@

For flow analysis, we need to analyse where people are going on what part of the day.
In this section we first discuss how we processed the data in order to find the locations people are heading to and then discuss how we visualise the data in order to show proper results.

@@

We processed the the data so that for both every origin and destination we have a unique identifier and the longitude and latitude.
We have done this using the open-source reconciliator at \url{https://github.com/irail/stations}.

>>>>

The iRail API is a XML/JSON HTTP API where each request on \url{http://api.irail.be} returns a response that can be used directly in an end-user app.
It contains four features:

\begin{itemize}
\item Route Planning (\url{http://api.irail.be/connections/{?from,to,date,time}}).
\item Next Departures (\url{http://api.irail.be/liveboard/{?station,date,time}}).
\item Train Status (\url{http://api.irail.be/vehicle/{?id,date}}).
\item List All Stations (\url{http://api.irail.be/stations/}).
\end{itemize}

@@

This dataset is compiled from the \emph{Apache} \emph{access.log} files generated between 2012 and 2015. Each data entry contains a: 
\begin{itemize}
  \item Timestamp,
  \item HTTP Status Code,
  \item Request Path (e.g., \url{/connections/?from=Ghent\&to=Antwerp})
  \item User-Agent (cfr. RFC2616\footnote{The User-Agent request-header field contains information about the user agent originating the request. This is for statistical purposes, the tracing of protocol violations, and automated recognition of user agents for the sake of tailoring responses to avoid particular user agent limitations -- \url{http://www.w3.org/Protocols/rfc2616/rfc2616-sec14.html}})
\end{itemize}

@@

Flow analysis involves the comparison of aggregated movement between distinct locations within a specific time frame. Data visualisation is typically employed to facilate in this process thus the input data must be transformed into a format that expresses the quantity and directional flow of human movment. In this section we describe the data transformation procedure and data visualisation technique  employed in our case study.

@@

We processed the the data so that for both every origin and destination we have a unique identifier and the geographic coordinates. This is facilitaed with the open-source reconciliator \todo{one liner that describes how this works} situated at \url{https://github.com/irail/stations}.
